Fluent statistical computing interfaces for biological data analysis

### 2020-04-15 Rmd/01-intro.Rmd
add paragraph

This thesis develops tools and frameworks to perform EDA as part of the
biological data science workflow...

## A grammar for genomic data analysis

@@

## Integration and representation of genomic data structures

>>>>

This thesis focuses on three core aspects of EDA as part of a biological data
science workflow: wrangling, integration and visualisation (in particular we 
focus on the exploration of genomics and transcriptomics data).
It is organised in the same manner that you would iterate back and
forth between these tasks  during an analysis. To begin you wrangle your data into a structure 
that you can understand and use; section \@ref(sec:tidygranges) introudces a
grammar-based framework for transforming genomics data that is described in 
chapter \@ref(ch:plyranges). Next, you integrate data and model outputs
over genomic regions to gain biological insight; \@ref(sec:ir) introduces a
framework for incorporating and discovering 'interesting' genomic regions,
described further in chapters \@ref(ch:fluentGenomics) and \@ref(ch:intron).
Third, you cycle between model-based representations and visualisations
of your data; section {#sec:va} introduces a visual analytics approach for
understanding non-linear dimension reduction techniques and is described in
detail in chapter \@ref(ch:tsne). Lastly, you take a step back and look at
the implications and limitations of your work; in chapter \@ref(ch:conclusion)
I describe the impacts of my work and plans for future research.

## A grammar for genomic data analysis {#sec:tidygranges}

@@

## Integration and representation of genomic data structures {#sec:ir}
